Quasars Probing Quasars IX. The Kinematics of the Circumgalactic Medium Surrounding $z\sim2$ Quasars

### 2017-09-22 QPQ9/Submit/response.txt

We thank the referee for pointing out the importance of accurate redshift measurements. We have addressed the
suggested additional work in the details to follow.

>2) The authors have not demonstrated that the measured 1-sigma dispersion measured in a mean stack is is a
>representative measure of the velocity spread observed between absorbing gas and the quasar redshift. This may not be
>the case if the absorbing components exhibit a non-Gaussian distribution about the quasar systemic redshift as has
>been seen in other studies (e.g. Lau et al. 2016 and Johnson et al. 2015). In particular, broad wings on the
>distribution will be suppressed in a stack even if they contain a significant amount of the power because the
>absorbing components can be narrow. This is a weakness of analysis based on stacks that could easily be remedied
>because previous QPQ papers published absorber redshifts and even component-by-component velocity structure when
>available. A figure showing this distribution is needed in this publication.

The distribution of absorbing components in velocity is non-Gaussian for each quasar-host associated system. However,
we have 30 absorption systems for CII analysis, and an even larger number of absorption systems for CIV and MgII
analyses. The number of individual components can only be larger. The central limit theorem applies and the
distribution of all absorbing components should tend toward Gaussian distribution. A component-by-component analysis
requires echellette or echelle resolution, which is a criterion for the QPQ8 sample. For this current work, we stack
spectra of all resolutions. Text has been added to explain the above and to refer the readers to specific figures in
QPQ8.

@@

We have added text to explain how redshifts are measured. We acknowledge the confusion in calling the line-centering
algorithm a centroiding method. Our algorithm calculates the mode of a line given by (3*median - 2*mean), applied to
the upper 60% of the emission line. Shen+16 states that difference between the peak and the centroid is not
significant, except for the broad line Hbeta, which we did not use in redshift measurements. We have further obtained
individual measurements of centroids and peaks in Shen+16 thru private communication. There is essentially no
difference between using the centroid versus using the peak for [OIII], and there is about 50 km/s
difference for MgII on average. We may expect the difference between a mode and a peak is even smaller.

In the first version of the submitted manuscript, there are two redshift measurement techniques in the z ~ 2 sample:
our custom line-centering algorithm, and the algorithm of Hewett&Wild10. We thank the referee for scrutinizing the
redshift measurement techniques, which helps strengthen our results. In this re-submitted manuscript, for all z > 1.6
sample we measure redshifts of all quasars using our own custom line-centering algorithm instead of adopting values
from Hewett&Wild10. After we purge the quasars whose redshift measurement is dominated by CIII], we find that on
average there is essentially no difference between the Hewett&Wild10 redshifts and our own measured redshifts.
Furthermore, Shen+16 has stated throughout the paper that their work is consistent with Hewett&Wild10 on redshift
estimates based on MgII emission and on the average systemic bias. Therefore, for the z ~ 1 sample, where either the
[OIII] or the MgII emission has good data quality, and where we do not measure an intriguing asymmetry in the average
absorption, we continue to adopt the Hewett&Wild10 redshifts.

@@

We have explained in the text that, our results cannot be severely biased by [OIII] redshifts. We have tried
replacing the [OIII] redshifts by MgII or Halpha redshifts, and found a similar centroid and dispersion in the stack.
MgII and Halpha are broader, but it has not been reported in any literature that they are more asymmetric.

>Major point 2:
>
>In Lau et al. 2016, the distribution of absorbing components about the quasar systemic redshift is non-Guassian and
>exhibits broad wings that contain significant portion of the optical depth at large velocities. In a mean stack, these
>wings can be suppressed so that the dispersion of the stacked absorption profile does not represent the actual
>velocity spread. For example, if absorbers are distributed in velocity around quasar hosts with a core component
>within |v|<200 km/s and a wing component within |v|=200-1000 km/s, then the wing component will be suppressed by a
>factor of ~8 relative to the core because narrow absorbers are being spread over a larger velocity range. The authors
>need to demonstrate that this is not an issue before adopting the 1-sigma dispersion in the stack as a measure of the
>kinematic spread of the absorbing gas. This is a general weakness of stacked measurements and raises the question of
>why the study does not show a histogram of the velocity differences between the quasar systemic and observed
>absorption centroids in individual cases where the S/N is sufficient. Previous QPQ papers reported absorber redshifts
>(Prochaska et al. 2014) and individual component measurements (Lau et al. 2016). It should therefore be
>straight-forward to measure the actual velocity distribution of absorption systems around quasars directly rather than
>relying on stacked measurements. The authors should include such a histogram in the revised paper.

As explained above, we have sufficient number of absorbing components that they should tend toward a Gaussian
distribution in the stack. We are able to model the stack by a Gaussian multiplied to a pseudocontinuum. Our visual
inspection does not hint at a broader component in the stack. QPQ7 reported the redshift of the strongest Lya
absorption within the search window. The QPQ7 sample has spectra of all resolutions. It requires echellette or
echelle resolution to identify the metal-associated absorbers. In QPQ8, a scatter plot of the optical depth weighted
centroid of the absorption systems is shown. In the Appendix of QPQ8, the absorption profiles of the individual
components are shown. We have counted 6 of them are at negative velocities, while 15 of them are at positive
velocities. text have been added to reflect these numbers.

@@

>Major point 3:
>
>The authors do not provide enough detail regarding the fit to the mean stack. In particular, for MgII and CIV two
>gaussian with fixed doublet separation and width are fit to the stack. However, no details on the doublet ratio range
>allowed are given. This is particularly important for CIV where the doublets are not well resolved in the stack.
>Consequently, the velocity centroid and doublet ratio will be degenerate and uncertainty due to this degeneracy must
>be addressed.

We thank the referee for pointing out the insufficient detail in the text. The doublet ratio is allowed to vary
between 2:1 to 1:1.

>Major point 4:
>The primary results of the paper are that (1) while the dispersion observed in the stack is large, galactic superwinds
>may not be required to explain the width and (2) the absorption is kinematically offset from the quasar systemic
>redshifts by ~+200 km/s. The authors interpret this offset as due to effects from partial obscuration of the quasar or
>finite quasar lifetimes and light-travel time under the assumption that gas is, on average, flowing away from the
>quasar host. In QPQ VII the CII covering fractions are observed to decrease rapidly from ~80% at projected distances
>of <200 kpc to 20% at 200-500 kpc and <10% at 500-1000 kpc. This rapid fall-off with projected distance suggests that
>the majority of the absorption arises in the quasar host halo. Consequently, motions due to Hubble flow are not likely
>to be significant. Conclusion (2) therefore requires significant outflows in the halo, inconsistent with conclusion
>(1). This discrepancy needs to be addressed in the discussion.

In QPQ8, we have estimated the random incidence of optically thick absorbers. Text has been added to reflect
these numbers. As our Monte Carlo simulations demonstrate, outflows are not required to reproduce the observed
amplitude and dispersion of the mean absorption.

@@

>Major point 5:
>
>Several papers in the literature that are cited are mis-represented in the introduction. In particular:
>
>Johnson et al. 2015 is cited as concluding that the large velocity of absorbing gas observed around quasars is due to
>outflows. This is not the case. The paper considers several possible explanations including large-scale structure,
>galaxy interactions, and outflows. The conclusion of the paper is that none of these possibilities can satisfactorily
>explain the observed properties of cool gas around quasars.
>
>Gauthier et al. 2013, Muzahid 2015, and Zahedy et al. 2016 exhibit velocity spreads of ~600, 300-400, and 600 km/s
>respectively, which is comparable with those observed in the QPQ survey, contrary to the claim in the paper. This
>inaccurate statement needs to be clarified and corrected.
>
>These misrepresentations combined with the fact that the paper applies redshift bias corrections from the literature
>that are not appropriate for their redshift measurement techniques indicates that the authors need to carefully review
>the paper and ensure that the citations to the literature are correctly represented and applied.

We thank the referee for clarifying the explanation to Johnson+15's results. We have updated the text to reflect that
outflows is only one possibility. Gauthier+13 is a single sightline, and the velocity width Dv90 of the MgII
absorber is less than the average of QPQ8 CII absorber. Muzahid+15 found an absorber with Dv90 less than 555 km/s in
OVI and NV, and still smaller for other ions. Zahedy+16's sample has average Dv90 smaller than that of QPQ8.

@@

>Minor issues:
>
>Introduction Section:
>
>1) When discussing inflows, the authors should cite Rubin et al. 2012
>2) The definition of h in this paper is not in accordance with the common convention and should be replaced with h_70
>to prevent the casual reader from being confused.
>3) Rudie et al. 2017 should be included in the references for systems with large velocity spread. This paper is
>highly relevant to the discussions in this manuscript.

We have cited Rudie+17 in our revised manuscript. As our focus is on absorbers in background sightlines, Rubin+12 is
less relevant. We intend that h = H_0 / (100 km s^-1 Mpc^-1), in accordance with the common convention, that is also
widely used in cosmology papers such as Kravtsov+17. We have state this scaling explicitly in our revised manuscript.
We thank the referee for above suggestions.

@@

>Analysis Section:
>1) The authors claim that it is not necessary to smooth the spectra before linearly interplating onto a 100 km/s
>pixel grid. This may be true for the low-resolution spectra but is untrue for the moderate and high resolution
>spectra used where linear interpolation onto a coarser pixel scale will have unpredictable results. The authors
>should test that this dues not actually change any results.

For each sightline, we overplotted the original absorption profile and that interpolated onto the common velocity
grid, and visually the overplots. We have confirmed to ourselves that the equivalent widths and the shapes of the
absorption profiles are preserved.

>2) The mean redshifted centroid in the CII profile is observed in the mean stack but not the median at a level that
>is in tension. The study does not address this discrepancy and does not provide sufficient reasoning for preferring
>the mean over the median when attempting to measure a centroid.

There is large intrinsic scatter in the CGM environments. In our revised manuscript, we update the sample to pairs
retrieved from the latest QPQ Survey database and we re-measure the redshifts originally adopted from HeWitt&Wild10.
With this sample the median CII statistic has a centroid +105+/-176 km/s. We prefer the mean over the median, as the
median statistic is less sensitive to absorption signals and does not preserve equivalent width. The median opacity at
any velocity channel can be rather small, since absorbers are spread out throughout the entire velocity window and are
discretized. The centroid measured from the median stack is thus subject to larger uncertainty.

@@

>3) It is quite odd that the quoted error in the centroid for the z=1 coadd is 388 km/s, larger than the 161 km/s
>dispersion. What is going on here? In addition, why would a shift be observed for z=2 quasars but not z=1 ones? The
>authors seem to take this as evidence that the redshift in the absorption centroid is real. I came to the opposite
>conclusions since accurate redshifts for low-z quasars are easier to come by.

The quoted uncertainty in the centroid is the standard deviation in the 10000 bootstrap realizations. The average
absorption of this stack is weak, and the measured dispersion too has a large intrinsic scatter. A shift is not
definitively observed in the 0.4 < z < 1.6 stack. It may be due to weaker average absorption, or it may be due to
lower average quasar luminosity should our interpretations be correct. The 0.4 < z < 1.6 quasars are largely SDSS
spectra, and we adopt redshifts taken from Hewett&Wild10, which are dominated by the [OIII] or the MgII emission-line.
The z ~ 2 quasars of our sample have MgII, [OIII], or Halpha emission-line redshifts. We do not consider that the
redshifts of the 0.4 < z < 1.6 quasars are more accurate, since the more precise [OIII] redshifts are only accessible
in SDSS spectral coverage for z < 0.84.

### 2017-09-22 QPQ9/Submit/qpq9_submit.tex
Updated the sample

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
We employ 112 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
absorption. The sample selects foreground quasars with precise redshift measurements, using 
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4}, 
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
motion and Hubble flow, and galactic-scale outflows are not required to explain the large 
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
The mean absorption centroids exhibit small redshift relative to the 
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid 
velocities of the individual absorption systems. We show that the observed offsets may be produced 
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the 
gas is not flowing into the galaxy.  
\end{abstract}

@@

With absorption-line spectroscopy of background sightlines, other researchers also have had 
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of 
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
$z\sim1$ quasars, and 
found large peculiar motions in the gas exceeding the expected virial velocity, which they 
interpret as quasar-driven outflows. However, the velocity spreads were not well quantified. Other 
existing studies that found large velocity spreads are limited to single sightlines with most of 
the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11}, or with gas tracing 
a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
the average velocity spread is smaller than that measured in QPQ8 
\citep[e.g., ][]{Gauthier13,Muzahid+15,Zahedy+16}.

@@

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][, hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched CGM 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 112 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Among the
sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10). For this
current work, we stack spectra of all resolutions instead of performing a component-by-component
analysis. Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
outflows from the central galaxy, presumably driven by recent star formation and/or active galactic
nuclei feedback; (ii) characterize the dynamics of the gas around these massive systems. We further
describe an aspect of this experiment that offers a unique opportunity to study galactic-scale
flows: we argue that, the anisotropic or intermittent radiation from the foreground quasars may
break the symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation
field is asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar
lifetime will result in different radiation fields impinged on the gas closer to versus further
away from the background quasar, due to different light travel times. \cite{KirkmanTytler08}
reported an asymmetry in \ion{H}{1} absorption on scales larger than the CGM, and gave similar
arguments on anisotropy or intermittence.

@@

We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec}, which includes the spectra from the quasar 
catalogs based upon the Sloan Digital Sky Survey Seventh Data Release \citep{Schneider+10} and the 
Twelfth Data Release \citep{Paris+17}. We only select pairs with $z_{\rm fg}$ measured by 
\cite{HewettWild10} using the \ion{Mg}{2}\,2800 emission-line, and we add the median blueshift of 
\ion{Mg}{2} from the systemic to these redshifts. We reach a final sample size of 112. 
Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
QPQ publications for the details on the emission-line centering algorithm, data reduction, and
continuum normalization (QPQ1; QPQ6; QPQ8).

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
$28\,{\rm km\,s^{-1}}$ and $29\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling 
errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
a common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than scatter in the flux of individual observations. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. The median 
statistic is less sensitive to outliers, however the averaged equivalent width is smaller and the 
analysis on the velocity field becomes more uncertain. In the following we present stacked spectra 
using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to analyze their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
skewed toward positive velocities. We have 33 pairs in the QPQ9 sample for \ion{C}{2} analysis
and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
of individual components can only be larger than the number of absorption systems. Hence, although
QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
individual quasar-host associated system. , the central limit theorem applies and the distribution
of all absorbing components should tend toward Gaussian distribution. To model the absorption, we
introduce a Gaussian profile while allowing a constant pseudo-continuum level to vary. We perform
$\chi^2$ minimization with each channel given equal weight. From the best-fit to the data, we
measure the centroid of the \ion{C}{2} stack to be $+196\,{\rm km\,s^{-1}}$ and the $1\sigma$
dispersion to be $313\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that contradicts the
standard expectation, while the dispersion suggests extreme kinematics. The median stack, on the
other hand, shows weaker absorption, and the Gaussian model has a centroid with smaller offset and
comparable dispersion.

@@

Given the small sample size, one must scrutinize the statistical significance of the measured 
velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
to model each bootstrap realization, and quote the standard deviation in the bootstrap 
realizations to be the scatter in the centroids of the data. The scatters 
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
find that 98\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper 
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
$\delta v<+424\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
absorption.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
velocity structure and again shows a positive offset $\approx+259\,{\rm km\,s^{-1}}$. We thus
conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
[\ion{O}{3}] emission-line.

@@

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
\includegraphics[width=2.5in]{f03.pdf}
\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
for the \ion{C}{2} mean stack. 98\% of the centroids are positively offset from $z_{\rm fg}$.}
\label{fig:histogram_cen}
\end{figure}

@@

\begin{thebibliography}{45}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

>>>>

\begin{abstract}
We examine the kinematics of the gas in the environments of galaxies hosting quasars at $z\sim2$. 
We employ 102 projected quasar pairs to study the circumgalactic gas of the foreground quasars in 
absorption. The sample selects foreground quasars with precise redshift measurements, using 
emission-lines with precision $\lesssim300\,{\rm km\,s^{-1}}$ and average offsets from the 
systemic redshift $\lesssim|100\,{\rm km\,s^{-1}}|$. We stack the background quasar spectra at the 
foreground quasar's systemic redshift to study the mean absorption in \ion{C}{2}, \ion{C}{4}, 
and \ion{Mg}{2}. We find that the mean absorptions exhibit large velocity widths 
$\sigma_v>300\,{\rm km\,s^{-1}}$. The observed widths are consistent with gas in gravitational 
motion and Hubble flow, and galactic-scale outflows are not required to explain the large 
widths. Furthermore, we find that the mean absorptions are asymmetric about the systemic redshift. 
The mean absorption centroids exhibit small redshift relative to the 
systemic $\delta v\approx+200\,{\rm km\,s^{-1}}$, with large intrinsic scatter in the centroid 
velocities of the individual absorption systems. We show that the observed offsets may be produced 
if (i) the ionizing radiation from the foreground quasars is anisotropic or intermittent; (ii) the 
gas is not flowing into the galaxy.  
\end{abstract}

@@

With absorption-line spectroscopy of background sightlines, other researchers also have had 
success in characterizing the flows of gas around galaxies. \cite{Rakic+12} found a net 
large-scale inflow around star-forming galaxies, or a Kaiser effect for gas on 
1\textendash2\,Mpc scales. \cite{Ho+17} found gas spiraling inward near the disk plane of 
star-forming galaxies on $<100$\,kpc scales. \cite{Johnson+15} studied the CGM surrounding 
$z\sim1$ quasars. They found large peculiar motions in the gas exceeding the expected virial 
velocity, with quasar-driven outflows being one possible explanation. However, we consider that 
their velocity spreads can be better quantified. Other 
existing studies that found large velocity spreads are limited to single sightlines with most of 
the gas within several hundred ${\rm km\,s^{-1}}$ \citep[e.g., ][]{Tripp+11,RudieNewmanMurphy17}, 
or with gas tracing 
a higher ionization state than the QPQ absorption systems \citep[e.g., ][]{Churchill+12}, or where 
the average velocity spread is smaller than that measured in QPQ8. In \cite{Gauthier+13}, where a 
single sightline is reported, the $\Delta v_{90}$ of the \ion{Mg}{2} absorption is less than the 
average of the QPQ8 \ion{C}{2} absorption. In \cite{Muzahid+15}, an absorber is found with 
$\Delta v_{90}$ smaller than $555\,{\rm km\,s^{-1}}$ in \ion{O}{6} and \ion{N}{5}, and still 
smaller for other ions. The \cite{Zahedy+16} sample likewise has average $\Delta v_{90}$ smaller 
than that of QPQ8.

@@

In this paper (hereafter QPQ9), we examine the flows of gas in the environments of massive 
galaxies hosting quasars. Our approach leverages a large dataset of quasar pairs 
\citep[][hereafter QPQ1]{QPQ1} to use the standard techniques of absorption-line spectroscopy 
with background quasars. These quasar pairs 
have angular separations that correspond to less than 300\,kpc projected separation at the 
foreground quasar's redshift. Our previous publications from these quasar pairs have established 
that these galaxies are surrounded by a massive, cool, and enriched CGM 
\citep[QPQ5, QPQ6, QPQ7:][]{QPQ5,QPQ6,QPQ7}. We have collected a sample of 102 background 
spectra that are paired with foreground quasars with precisely measured redshifts. Among the
sightlines in the QPQ9 sample, 13 have spectral resolution $R>5000$ from echellette or echelle
observations, and have been analyzed separately in QPQ8 (see their Figure 8, 9, and 10, and their 
Appendix). In QPQ8, where the individual metal-bearing absorption components are resolved, 15 out 
of the 21 components are at positive velocities relative to the systemic redshift. For this
current work, we stack spectra of all resolutions instead of performing a component-by-component
analysis. Our primary scientific interests are twofold: (i) search for signatures of galactic-scale
outflows from the central galaxy, presumably driven by recent star formation and/or active galactic
nuclei feedback; (ii) characterize the dynamics of the gas around these massive systems. We further
describe an aspect of this experiment that offers a unique opportunity to study galactic-scale
flows: we argue that, the anisotropic or intermittent radiation from the foreground quasars may
break the symmetry in the velocity field of circumgalactic absorbers. If the ionizing radiation
field is asymmetric, the absorbers may also distribute asymmetrically. Alternatively, finite quasar
lifetime will result in different radiation fields impinged on the gas closer to versus further
away from the background quasar, due to different light travel times. \cite{KirkmanTytler08}
reported an asymmetry in \ion{H}{1} absorption on scales larger than the CGM, and gave similar
arguments on anisotropy or intermittence.

@@

We further add to the QPQ dataset with quasar pairs selected from the public dataset of 
igmspec\footnote{https://github.com/specdb/igmspec} \citep{Prochaska+17}, which includes the 
spectra from the quasar catalogs based upon the Sloan Digital Sky Survey Seventh Data Release 
\citep{Schneider+10} and the Twelfth Data Release \citep{Paris+17}. We only select pairs with 
$z_{\rm fg}$ measurable using a robust \ion{Mg}{2}\,2800 emission-line. 
We reach a final sample size of 102. 
Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
QPQ publications for the details on the emission-line centering algorithm, data reduction, and
continuum normalization (QPQ1; QPQ6; QPQ8).

@@

\begin{figure}
%\includegraphics[width=3.5in]{Figures/fig_stacks_and_fits.pdf}
\includegraphics[width=3.5in]{f02.pdf}
\caption{Mean and median absorption centered at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 of the foreground quasars for all QPQ9 pairs. The composites are shown in thin, 
black. Overplotted on the composites are Gaussian fits, normalized to pseudo-continua far away 
from a velocity of $0\,{\rm km\,s^{-1}}$ relative to $z_{\rm fg}$, and are shown in thick, blue. 
For the doublets, a second Gaussian with a fixed mean separation and a tied standard deviation is 
included in the modeling. The absorptions frequently exhibit large velocity widths. The dashed 
lines mark the centroids, which show small positive velocity offsets from $z_{\rm fg}$. The 
$1\sigma$ modeling error for the centroid and dispersion of the \ion{C}{2} mean stack are 
$19\,{\rm km\,s^{-1}}$ and $20\,{\rm km\,s^{-1}}$ respectively, which is also the typical modeling 
errors of the other stacks.
}
\label{fig:stacks_and_fits}
\end{figure}

We create composite spectra that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra of background quasars are 
shifted to the rest-frame of the foreground quasars at the transitions of interest. Each spectrum 
has been linearly interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For a velocity bin of this size, it is unnecessary to smooth the data to 
a common spectral resolution. The individual spectra are then combined with a mean or a median 
statistic. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles, i.e.\ we do not weight the spectra by the measured S/N near the 
metal ion transitions. Scatter in the stacked spectra is dominated by randomness in the CGM rather 
than scatter in the flux of individual observations. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. The median 
statistic is less sensitive to outliers, however the median opacity at any velocity channel is 
rather small, since the discrete absorbers are spread throughout the entire velocity window. The 
analysis on the median velocity field is thus subject to larger uncertainty. In the following we 
present stacked spectra using both the mean and the median statistic.

In Figure~\ref{fig:stacks_and_fits}, we present mean and median stacks of \ion{C}{2}\,1334, 
\ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 absorption of the QPQ9 sample. We focus on the 
analysis results of the \ion{C}{2} mean stack. \ion{C}{4} and \ion{Mg}{2} are doublet transitions 
and it is more challenging to analyze their kinematics.
%To assess the average absorption of these transitions,
%we have combined the data with a novel technique.
%We have fitted the combined dataset using a cubic b-spline
%with knots at every 100\,kms.  We weighted each data
%point by the velocity width of the pixel to insure that 
%each sightline makes an equal contribution to the stack.
%These b-spline profiles are presented in the figure
%and a trivial integration gives the reported equivalent
%widths.
%[consider down-weighting systems with $<3\sigma$ EW]
%[Comnent on EW from 'standard' technique]
Two results are evident in Figure~\ref{fig:stacks_and_fits}: (i) the mean \ion{C}{2} stack 
exhibits excess absorption spanning a large velocity width; (ii) the mean absorption is likely 
skewed toward positive velocities. We have 30 pairs in the QPQ9 sample for \ion{C}{2} analysis
and an even larger number of pairs for \ion{C}{4} and \ion{Mg}{2} analyses, and the total number
of individual components can only be larger than the number of absorption systems. Hence, although
QPQ8 showed the distribution of absorbing components in velocity is non-Gaussian for each
individual quasar-host associated system, the central limit theorem applies and the distribution
of all absorbing components should tend toward Gaussian distribution. A visual inspection of the 
stack confirms that a broader absorption component is not apparent. Therefore, to model the 
absorption, we may introduce a Gaussian profile while allowing a constant pseudo-continuum level 
to vary. We perform $\chi^2$ minimization with each channel given equal weight. From the best-fit 
to the data, we measure the centroid of the \ion{C}{2} stack to be $+254\,{\rm km\,s^{-1}}$ and 
the $1\sigma$ dispersion to be $299\,{\rm km\,s^{-1}}$. The centroid suggests an asymmetry that 
contradicts the standard expectation, while the dispersion suggests extreme kinematics. The median 
stack, on the other hand, shows weaker absorption, and the Gaussian model has a centroid with 
smaller offset and comparable dispersion.

@@

Given the small sample size, one must scrutinize the statistical significance of the measured 
velocity offsets. To assess the statistical significance, we perform a boostrap analysis by 
randomly resampling from the full sample 10000 times. We introduce a Gaussian absorption profile 
to model each bootstrap realization, and quote the standard deviation in the bootstrap 
realizations to be the scatter in the centroids of the data. The scatters 
$\approx100\,{\rm km\,s^{-1}}$ are comparable to the measured offsets, indicating large intrinsic 
variation in quasar CGM environments (see also QPQ8). In Figure~\ref{fig:histogram_cen}, we show 
the distribution of the absorption centroids from bootstrapping on the \ion{C}{2} mean stack. We 
find that 99\% of the centroids are at positive velocities. We place a generous $3\sigma$ upper 
limit to the small offset of the centroid from $z_{\rm fg}$ for the \ion{C}{2} mean absorption at 
$\delta v<+509\,{\rm km\,s^{-1}}$. Given the large intrinsic scatter, we do not attempt to explore
whether there exists relative asymmetry among the \ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} 
absorption.

One may also ask whether the measured positive offsets come from systematic bias in redshift 
measurements due to the Baldwin effect \citep{Baldwin77}. \cite{Shen16} reported that, the 
[\ion{O}{3}] emission of $z\sim2$ quasars is more asymmetric and weaker than that in typically 
less luminous low-$z$ quasars. To test for this potential source of bias, we create another mean 
stack at \ion{C}{2}\,1334 by replacing the [\ion{O}{3}] redshifts by a redshift measured from the
more symmetric \ion{Mg}{2} or H$\alpha$ emission when available. We are able to replace for 11 out
of the 15 systems with [\ion{O}{3}] redshifts in the original sample. The new stack is similiar in
velocity structure and again shows a positive offset $\approx+319\,{\rm km\,s^{-1}}$. We thus
conclude that our algorithm for measuring redshifts is not severely biased by the blue wing of the
[\ion{O}{3}] emission-line.

@@

\begin{figure}
%\includegraphics[width=2.5in]{Figures/fig_histogram_cen.pdf}
\includegraphics[width=2.5in]{f03.pdf}
\caption{Histogram of the absorption centroids of 10000 bootstrap realizations of the data sample 
for the \ion{C}{2} mean stack. 99\% of the centroids are positively offset from $z_{\rm fg}$.}
\label{fig:histogram_cen}
\end{figure}

@@

\begin{thebibliography}{46}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Prochaska}(2017)}]{Prochaska+17}
{Prochaska}, J.~X. 2017, Astronomy and Computing, 19, 27
